A (sun)Shiny Recreation of the New York Times \n Weather Chart

### 2017-04-18 Paper.Rmd
web scraping section added

>>>>

Our first step in recreating The New York Times interactive weather chart was scraping the data from the web. We decided to scrape our data from [Weather Underground](https://www.wunderground.com/). This site is a weather web service that provides real-time and historical weather information. The majority of their weather data comes from 1602 stations operating at airports across the US. For this project, we scraped temperature data for 10 cities in the Midwest: Chicago, Columbus, Des Moines, Detroit, Fargo, Madison, Minneapolis, Omaha, Sioux Falls, and St. Louis.

We decided to scrape our data from Weather Underground because they supplied the necessary temperature data that we would need to recreate The New York Times chart in a refined table for multiple cities across the US. Along with that, the url was easy to update in a function according to year and city. Figure 1 is a screen shot for the webpage of Des Moines, IA for January 1, 2015. The url for this webpage is https://www.wunderground.com/history/airport/KDSM/2015/1/1/DailyHistory.html. In this url, "KDSM" indicates the Des Moines airport. Following that is the year, month, and date. These are the only segments of the url that change according to specified cities (i.e. airports) and days.

![Screen shot of Weather Underground site for Des Moines, IA on Janurary 1, 2015](weather_underground_screenshot.png)

For each city, two functions were run to scrape the data. The first function scraped the daily actual mean, maximum, and minimum temperatures. On the Weather Underground webpage, this is the *Actual* column seen in Figure 1. The maximum and minimum daily actual temperatures would later become the lower and upper bounds of the daily temperature layer on our graphic. Daily temperatures were scraped for each day starting on January 1, 1950 and ending on March 31, 2017. The second function scraped the historical average mean, maximum, and minimum temperatures as well as the record maximum and minimum for each day. The record years were also recorded with the record maximum and minimum. On the Weather Underground webpage, this is the *Average* and *Record* columns seen in Figure 1. The reason behind using two functions to scrape the data was due to efficiency. The historical averages and daily records only needed to be scraped for one year (366 days) while the daily actual temperatures needed to be scraped for all years (over 24,000 days).

Along with the historic temperature data, our Shiny app scrapes the current temperature given by Weather Underground for a specified city. This app will be described in later sections. This tempurature then becomes a point on our final graphic. As an example, the current temperature for Des Moines can be scraped from https://www.wunderground.com/US/IA/Des_Moines.html. By changing the state and city in this url, we can scrape the current temperature for any city that Weather Underground reports.

Web scraping was the most time consuming step of our project. It took approximately 7-8 hours to run our two functions that scrape the historical temperature data for each city. This is one of the main reasons why we only scraped data for 10 cities. If we had the time and computing power, we would like to have created our functions to input a vector of all 1602 Weather Underground airport codes and output one large data frame. If this were the case, we would most likely have to switch to a different software other than R.
